Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{}

### 2020-06-05 paper-v1.tex
Updates from Overleaf

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case
An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

@@

\subsubsection{Traditional editorial process}
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editor is assigned to the manuscript: at this stage the assessment of the paper concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item

\end{enumerate}2. 3. The editorial team decides whether to send the manuscript out to review. If the decision is not to send the manuscript for review, the editor contacts the author with the decision. 4. The editor assigns potential reviewers to the manuscript and the author is notiﬁed. 5. Reviewers agree to review the manuscript. 6. Reviewers submit their reports to the editor. 7. The editorial team discusses the reports and the editor makes the ﬁnal decision. This process may involve further consultation with the reviewers and editor-mediated communications between the reviewers. 8. The editor contacts the author with the decision. 9. If the decision is negative, the author can choose to transfer their manuscript to another journal. If the manuscript was peer reviewed the referee comments are also transferred. Please see our Manuscript Transfer FAQ for more information about this service.
\subsection{Related work}

@@

\section{System concept}
For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers. The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.

@@

Anonymity
Accountability
Reputation
Reward
Gamification model

open identities open reports open participation open interaction open platform ('decoupled review')
Basic architecture 
When authors of a paper submit their draft to an open access journal or preprint, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor. Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content. If the reviews are accepted (bounty fulfillment), reviewers awarded a token, an internal digital currency specific for this bounty, called ‘ANT’. The ideal scenario envisages multiple contributions both from the reviewers actors and the editors actors. To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].
Scenario 1 (journal-dependent)
Scenario 2 (community-driven): peer-review is decoupled from journal

\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Bounty}
AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].

\begin{lstlisting}[language=Solidity]

pragma solidity 0.6.8;

import "@openzeppelin/contracts/access/AccessControl.sol";

contract AntsReviewRoles is AccessControl {

/// Roles
bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");

}
\end{lstlisting}

In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.

>>>>

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent blockchain engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case
An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

@@

\subsubsection{Traditional peer-review process}
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves. 
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. 
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

\end{enumerate}

\subsection{Related work}

@@

\section{System concept}
For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers. The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
Anonymity
Accountability
Reputation
Reward
Gamification model

open identities open reports open participation open interaction open platform ('decoupled review')

@@

\subsubsection{AnstReview process: scenario 1  (journal-dependent)}\\

\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting. 
\end{enumerate}
When authors of a paper submit their draft to an open access journal or pre-print, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor. Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content. If the reviews are accepted (bounty fulfillment), reviewers awarded a token, an internal digital currency specific for this bounty, called ‘ANT’. The ideal scenario envisages multiple contributions both from the reviewers actors and the editors actors. To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].

Scenario 2 (community-driven): peer-review is decoupled from journal
or to the pre-print service or to an hypothetical AntsReview platform).
\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network, ERC20, AZTEC Protocol, IPFS, Proof of Existence, DAO, ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Bounty}

\begin{lstlisting}[language=Solidity]
pragma solidity 0.4.16;

contract TestContract {

	string private myString = "foo";

	function getString() constant returns (string) {
	    return myString;
	}

	function setString (string _string) {
	    myString = _string;
	}
}
\end{lstlisting}
